Grocery Pricing Strategies: An Analysis of Vendor Positioning and Market Dynamics

### 2024-11-14 paper/paper.qmd
finalize paper

>>>>

Our ability to establish a casual relationship in the data is limited due to lack of experimental design. Although a lack of experimental design does diminish our ability to infer causality, it only does so to a certain degree [@tellingstories]. To further uncover the causal relationships between vendor positioning and its market dynamics, experiments such as a regression discontinuity design or difference in differences design can be employed. However, these designs require a careful consideration of the structure of our dataset and identification of potential biases.
